Combined Task and Motion Planner through an Interface Layer

### 2015-04-29 documentation/draft.tex
pose generator works for pickup

\title{Combined Task and Motion Planner through an Interface Layer}
\author{Alex Gutierrez (ragtz@mit.edu), Bianca Homberg (bhomberg@mit.edu), and Veronica Lane (vmlane@mit.edu)}

@@

\subsection{Results}
The goal of each test was to move the green block, at the center of a grid of blocks, to a goal surface. 
We tested a variety of different grid shapes, including a square grid, an X, a cross, and lines. 
We tested each grid shape over a range of sizes ranging from 3 to 13. ref{fig-benchmarks} 
The most difficult benchmark we tested was the 13x13 square grid. Larger tests caused the FF planner to segfault.

>>>>

\title{Combined Task and Motion Planner through an Interface Layer}
\author{Alex Gutierrez (ragtz@mit.edu), Bianca Homberg (bhomberg@mit.edu), \\and Veronica Lane (vmlane@mit.edu)}

@@

\subsection{Results}
\begin{figure}[t]
	\centering
	\subfloat{\includegraphics[width=.45\linewidth]{figures/bvm}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{figures/bvt}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{figures/bvrt}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{figures/ovm}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{figures/ovt}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{figures/ovrt}}
	\qquad
	\subfloat{\includegraphics[width=.45\linewidth]{figures/square}}
	\caption{Benchmarking plots\label{fig:benchmarkPlots}}
\end{figure}
The goal of each test was to move the green block, at the center of a grid of blocks, to a goal surface. 
We tested a variety of different grid shapes, including a square grid, an X, a cross, and lines. 
We tested each grid shape over a range of sizes ranging from 3 to 13. ref{fig-benchmarks} 
The most difficult benchmark we tested was the 13x13 square grid. Larger tests caused the FF planner to segfault. As seen in \ref{fig:benchmarkPlots}, as the size of the problem increases the number of calls increases.
